### 2019-12-31 paper_stats.Rmd
move project over from main file

---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: style.1.docx
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 5 * 1.67, fig.height = 5)

  load("scripts/models_dec_2019.RData")

  library(sjPlot)
  library(tidyverse)
  library(broom)

```

# Statistical methods

Continuous variables were described by their means and SDs, medians and IQRs, and their range; while categorical variables were described by their counts and percentages in each category. Average treatment effects were estimated using mixed effects models with a random effect for participant. All reported models were adjusted for the sex of the participant (to correspond to the sex-stratified randomization lists). We also estimated a model with an added period effect, and another that also included an adjustment for period-specific baseline values of the outcome measure (REF). Following advice from Senn (REF), we did not formally test for a carry-over effect. All model-based estimates are reported with 95% CIs and p-values based on conditional F-tests with Kenward-Roger degrees of freedom (REF). We did not apply any adjustment for multiple testing, but have provided enough information for the reader to do so it they wish. Data were analysed on an intent-to-treat basis (i.e. without consideration for intervention compliance).

To evalaute the possilbity of heterogeneity of treatment effects, we

All analyses were conducted using R language for statistical computing software V3.6.0 (2019-04-26). We used the lme4 package (REF) to estimate mixed effects models; ggplot2 (REF) to generate plots; and sjPlot to produce tables of model results. All anonymized data and the code used to analyze it and generate outputs can be found on the Open Science Framework (https://osf.io/zq4y9/).

Table 1. Respondent characteristics
```{r table1_data}

  descript <- select(
    data,
    sequence, sex, age_screening, height_m, weight_kg_screen, bmi_screening, 
    sbpscreening, dbpscreening, smoking_ever, alcohol_consumption,
              physical_mins, tv_hours, sleep_hours, occupation,
              educationcategory) %>%
    mutate(sex = factor(sex, labels = c("Male", "Female")),
           smoking_ever = factor(smoking_ever, labels = c("No", "Yes")),
           alcohol_consumption = factor(alcohol_consumption, 
                                        labels = c("No", "Yes")),
           occupation = factor(occupation),
           educationcategory = factor(educationcategory))

```

```{r table1_describe}

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% knitr::kable()

```

Table 2. Blood pressure outcomes
```{r}

  model_list <- list(me_sbp_bl, me_c_sbp_bl, 
                     me_dbp_bl, me_c_dbp_bl)
  data_list  <- list(me_sbp_df, me_c_sbp_df, 
                     me_dbp_df, me_c_dbp_df)
  varnames <- c("SBP", "C SBP", "DBP", "C DBP")
  measures <- rep(c("SBP", "DBP"), each = 3)

# Just print the estimates and 95%CI from the models  
  des_est <- function(model){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3)) %>%
      filter(term == "tx2")

    return(paste0(x$estimate, " (", x$ll, " to ", x$ul, ")"))
  }

# lapply(model_list, des_est)

# Produce a dataframe of the within-person differences

  within_diffs <- function(data, var){
    select(data, subj_id, tx, ep) %>% 
    mutate(tx = factor(tx, labels = c("Control", "Active"))) %>%
    spread(tx, ep) %>% 
    mutate(effect = Active - Control) %>% 
    filter(!is.na(effect)) %>%
    summarise(Mean_diff = signif(mean(effect, na.rm = TRUE), 2),
              SD_diff = signif(sd(effect, na.rm = TRUE), 2), 
              n_diff = n(), 
              Outcome = var) %>% 
    select(Outcome, n_diff, Mean_diff, SD_diff) %>%
    return()
  }

  difs_df <- do.call(bind_rows, map2(data_list, varnames, within_diffs)) %>%
    mutate(Outcome = factor(Outcome, levels = varnames))

  difs_df$Estimate <- unlist(lapply(model_list, des_est))

  get_p <- function(model){
    x <- sjstats::p_value(model) %>% filter(term == "tx2")
    return(signif(x$p.value, 2))
    }

  difs_df$p <- unlist(map(model_list, get_p))

  means_sds <- function(data, var){
    full_join(
      select(data, subj_id, tx, ep) %>%
        mutate(tx = factor(tx, labels = c("Control", "Active"))) %>%
        filter(tx == "Control" & !is.na(ep)) %>% 
        summarise(n_control = n(), 
                  mean_control = signif(mean(ep, na.rm = TRUE), 2), 
                  sd_control = signif(sd(ep, na.rm = TRUE), 2), 
                  Outcome = var), 
       select(data, subj_id, tx, ep) %>%
        mutate(tx = factor(tx, labels = c("Control", "Active"))) %>%
        filter(tx == "Active" & !is.na(ep)) %>% 
        summarise(n_active = n(), 
                  mean_active = signif(mean(ep, na.rm = TRUE), 2), 
                  sd_active = signif(sd(ep, na.rm = TRUE), 2), 
                  Outcome = var), 
      by = "Outcome"
    ) %>%
    return()
  }

  means_df <- do.call(bind_rows, map2(data_list, varnames, means_sds))

  table_df <- full_join(means_df, difs_df, by = "Outcome") %>%
    select(Outcome, everything())

  knitr::kable(table_df)

```

Figure 1. Mixed-effect model estimated treatment effects for blood pressure outcomes. 
```{r}
# Produce a data frame of the estimates and 95%CI from the models and plot it

  des_est2 <- function(model, varname){
    x <- broom::tidy(model) %>% 
      mutate(estimate = signif(estimate, 2), 
             ul = signif(estimate + (1.96 * std.error), 3), 
             ll = signif(estimate - (1.96 * std.error), 3), 
             var = varname) %>%
      filter(term == "tx2")

    return(x)
  }

  primary_df <- do.call(bind_rows, map2(model_list, varnames, des_est2)) %>%
    mutate(measure = rep(c("SBP", "DBP"), each = 2)) %>%
    mutate(var = factor(var, levels = varnames))

  ggplot(primary_df,
         aes(x = var, y = estimate, ymax = ul, ymin = ll, color = measure)) +
    geom_pointrange() +
    theme_minimal() +
    xlab("") +
    ylab("mmHg") +
    geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
    scale_color_brewer(guide = FALSE, palette = "Set1")

    ggsave("plots/primary/all.pdf", width = 33.867, height = 19.05, units = "cm",
         scale = 0.6, dpi = 600)

```

Figure 2. Change in systolic blood pressure across the two study periods
```{r}

  mutate(
    sbp, 
    treatment_p1 = factor(treatment_p1, labels = c("Control", "Active")), 
    treatment_p2 = factor(treatment_p2, labels = c("Control", "Active")) 
  ) %>% 
  cross_plot("SBP (mmHg)")

  ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
         scale = 0.6, dpi = 600)
```

Heterogenity

```{r}

# https://zenodo.org/record/1239539 code

  var_ratio <- function(df, var_lab, logged, ...){

    if(logged == "Yes"){

    data <- select(df, subj_id, tx, ep) %>% 
            mutate(ep = log(ep)) %>%
            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
            filter(!is.na(ep)) %>%
            spread(tx, ep) %>% 
            mutate(effect = Active - Control) %>% 
            filter(!is.na(effect)) 
    }

    if(logged == "No"){

    data <- select(df, subj_id, tx, ep) %>% 
            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
            filter(!is.na(ep)) %>%
            spread(tx, ep) %>% 
            mutate(effect = Active - Control) %>% 
            filter(!is.na(effect)) 
    }

    sdx <- sd(data$Active, na.rm = TRUE) 
    sdy <- sd(data$Control, na.rm = TRUE) 
    n   <- nrow(data)
    rho <- cor(data$Active, data$Control)

    Qx <- sdx^2*(n-1)            
    Qy <- sdy^2*(n-1)
    Qxy <- rho*sdx*sdy*(n-1)
    num <- (Qx-Qy)*sqrt(n-2)          # Statistic numerator
    den <- 2*sqrt(Qx*Qy-Qxy^2)        # Statistic denominator
    Qest <- num/den # T

    # LL2 <- qt(0.025, n-2)
    # UL2 <- qt(0.975, n-2)
    # greater.var.outQ <- sum(Qest < LL2) 
    # lower.var.outQ <- sum(Qest > UL2)

    if(Qest < 0){p <- pt(Qest, n-2) * 2}
    if(Qest > 0){p <- pt(Qest, n-2, lower.tail = FALSE) * 2}

    data <- data_frame(var = var_lab, 
                       vr = signif(sdx^2/sdy^2, 2), 
                       p = round(p, 3))

    return(data)

    }

  var_ratio(sbp, "SBP")

  data_list <- list(sbp, dbp, c_sbp, c_dbp, art_stif, glu, hdl, ldl, oxldl,
                    pwa_augment, tag, tchol)
  varnames <- c("SBP", "DBP", "Central SBP", "Central SBP", 
                "Arterial Stiffness", "Glucose", "HDL", "LDL", "OxLDL", 
                "PWA Augment", "TAG", "Total Cholesterol")

  vrs_df <- do.call(bind_rows, map2(data_list, varnames,  var_ratio))

  vrs_df

```

```{r hdl_variance_plot}

  mutate(hdl, tx = factor(tx, labels = c("Control", "Active"))) %>%
  filter(!is.na(ep)) %>%
  ggplot(aes(x = log(ep), fill = tx)) +
    geom_density(alpha = 0.5, color = "black") +
    theme_minimal() +
    xlab("HDL") +
    ylab("Density") +
    scale_fill_brewer("", palette = "Set1")

```

```{r all_distributions}

  dist(sbp, "SBP (mmHg)") +
    ggtitle("Systolic Blood Pressure")

  dist(dbp, "DBP (mmHg)", logged = "no") +
    ggtitle("Diastolic Blood Pressure")

  dist(oxldl, "Log(OXLDL)", logged = "yes") +
    ggtitle("OXDL")

  dist(art_stif, "Arterial Stiffness", logged = "no")+
    ggtitle("Arterial Stiffness")

  dist(glu, "Glucose", logged = "no") +
    ggtitle("Glucose")

  dist(ldl, "LDL", logged = "no") +
    ggtitle("LDL")

  dist(hdl, "Log(HDL)", logged = "yes") +
    ggtitle("HDL")

  dist(tchol, "Log(TCHOL)", logged = "yes")+
    ggtitle("Total cholesterol")

  dist(tag, "Log(TAG)", logged = "yes")+
    ggtitle("TAG")

  dist(pwa_augment, "PWA Augment", logged = "no")+
    ggtitle("Diastolic Blood Pressure")

```

### 2019-12-31 supplement.Rmd
move project over from main file

---
title: "supplmental"
output: html_document
---

## Blood pressure

```{r, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 5 * 1.67, fig.height = 5)

  library(tidyverse)
  source("scripts/functions.R")
  load("scripts/models_july_2019.RData")

  library(sjPlot)

```

Table 3. Mixed-effects model estimates for systolic blood pressure (mmHg)

```{r}

# SBP

  labs <- c("Intercept", "Treatment", "Sex", "Period")

  tab_model(
    me_sbp, me_sbp_p, me_sbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_sbp.html",
    pred.labels = c(labs, "SBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 1. Mixed-effects model estimates for diastolic blood pressure (mmHg)

```{r}

# DBP

  tab_model(
    me_dbp, me_dbp_p, me_dbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_dbp.html",
    pred.labels = c(labs, "DBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )
```

S-Table 2. Mixed-effects model estimates for oscillatory systolic blood pressure (mmHg)
```{r}

# OCS SBP

  tab_model(
    me_osc_sbp, me_osc_sbp_p, me_osc_sbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_osc_sbp.html",
    pred.labels = c(labs, "OSC SBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 3. Mixed-effects model estimates for oscillatory diastolic blood pressure (mmHg)

```{r}

# OCS DBP

  tab_model(
    me_osc_dbp, me_osc_dbp_p, me_osc_dbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_osc_dbp.html",
    pred.labels = c(labs, "OSC DBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 4. Mixed-effects model estimates for central systolic blood pressure (mmHg)

```{r}

# C SBP

  tab_model(
    me_c_sbp, me_c_sbp_p, me_c_sbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_c_sbp.html",
    pred.labels = c(labs, "C SBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 5. Mixed-effects model estimates for central diastolic blood pressure (mmHg)

```{r}

# C DBP

  tab_model(
    me_c_dbp, me_c_dbp_p, me_c_dbp_bl,
    p.val = "kr",
    file = "tables/primary/table_me_c_dbp.html",
    pred.labels = c(labs, "C DBP Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

## Other outcomes

S-Table 6. Mixed-effects model estimates for OXLDL

```{r}
# OXLDL ####

  tab_model(
    me_oxldl, me_oxldl_p, me_oxldl_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_oxldl.html",
    pred.labels = c(labs, "OXLDL Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 7. Mixed-effects model estimates for arterial stiffness

```{r}

# Arterial Stiffness ####

  tab_model(
    me_art_stif, me_art_stif_p, me_art_stif_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_art_stif.html",
    pred.labels = c(labs, "Stiffness Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 8. Mixed-effects model estimates for fasting glucose

```{r}

# Fasting glucose ####

  tab_model(
    me_glu, me_glu_p, me_glu_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_glu.html",
    pred.labels = c(labs, "Glucose Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 9. Mixed-effects model estimates for LDL

```{r}

# LDL ####

  tab_model(
    me_ldl, me_ldl_p, me_ldl_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_ldl.html",
    pred.labels = c(labs, "LDL Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 10. Mixed-effects model estimates for HDL

```{r}

# HDL ####

  tab_model(
    me_hdl, me_hdl_p, me_hdl_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_hdl.html",
    pred.labels = c(labs, "HDL Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 11. Mixed-effects model estimates for total cholesterol

```{r}

# TCHOL ####

  tab_model(
    me_tchol, me_tchol_p, me_tchol_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_tchol.html",
    pred.labels = c(labs, "TCHOL Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 12. Mixed-effects model estimates for TAG

```{r}

# TAG ####

  tab_model(
    me_tag, me_tag_p, me_tag_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_tag.html",
    pred.labels = c(labs, "TAG Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

S-Table 13. Mixed-effects model estimates for PWA augment

```{r}

# PWA Augment ####

  tab_model(
    me_pwa_augment, me_pwa_augment_p, me_pwa_augment_bl,
    p.val = "kr",
    file = "tables/secondary/table_me_pwa_augment.html",
    pred.labels = c(labs, "PWA AUGMENT Baseline"),
    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
    )

```

### 2019-12-31 scripts/01_project.R

@@ -1,0 +1,14 @@
+
+
+  source("scripts/functions.R")
+
+  source("scripts/data.R")
+
+  source("scripts/primary_outcome.R")
+
+  source("scripts/secondary_outcomes.R")
+
+  save.image(file = "scripts/models_dec_2019.RData")
+
+
+

### 2019-12-31 scripts/02_functions.R

@@ -1,0 +1,623 @@
+
+
+
+# Outcome data prep ------------------------------------------------------------
+
+# Pull the key study variables (time, period, tx, id) and an outcome, reshape to
+# long, and tidy up labels.
+
+  outcomes <- function(df, variable, ...){
+
+    df <- select(df, -contains("fwo"), -(contains("_mc_"))) %>%
+      gather(time, value, starts_with(variable)) %>%
+      select(sequence, treatment_p1, treatment_p2, time, value, subj_id,
+             sex) %>%
+      mutate(sequence = factor(sequence),
+             treatment_p1 = factor(treatment_p1),
+             treatment_p2 = factor(treatment_p2))
+
+    df$time <- gsub(variable, "", df$time)
+
+    times <- c("b_p1", "ep_p1", "b_p2", "ep_p2")
+
+    df <- mutate(df, time = factor(time, levels = times))
+
+    df$period[grepl("_p1", df$time)] <- "First"
+    df$period[grepl("_p2", df$time)] <- "Second"
+
+    bp <- grepl("b_p",  df$time)
+    ep <- grepl("ep_p", df$time)
+
+    df$timing[bp] <- "Baseline"
+    df$timing[ep] <- "EoP"
+
+    df$bl[bp] <- df$value[bp]
+    df$ep[ep] <- df$value[ep]
+
+    p1 <- df$period == "First"
+    p2 <- df$period == "Second"
+    df$tx[p1] <- df$treatment_p1[p1]
+    df$tx[p2] <- df$treatment_p2[p2]
+
+    df <- filter(df, !is.na(time)) %>%
+      arrange(subj_id, period, timing) %>%
+      select(subj_id, sequence, period, timing, tx, value, everything()) %>%
+      mutate(period = factor(period),
+             timing = factor(timing),
+             tx  = factor(tx, labels = c("Control", "Active")))
+
+    df$time2 <- factor(df$time, labels = c("p1_b", "p1_ep",
+                                           "p2_b", "p2_ep"))
+
+    return(df)
+  }
+
+# Outcome cross-over plot ####
+
+  cross_plot <- function(df, ylabel,logged = c("yes", "no"), ...){
+
+    if(logged == "no"){
+
+    return(ggplot(df, aes(x = time2, y = value, group = subj_id)) +
+      geom_line(data = filter(df, as.numeric(time) < 3), alpha = 0.2,
+                aes(color = treatment_p1)) +
[…]

### 2019-12-31 scripts/03_data.R

@@ -1,0 +1,66 @@
+
+  library(tidyverse)
+  source("scripts/functions.R")
+
+# Data -------------------------------------------------------------------------
+
+  data <- haven::read_spss("data/data.sav")
+
+# Notes from reading the protocol
+
+# SBP is the primary. We will also look at other CVD factors.
+# Power was based on SPB 135 sd 3. Is that SD of 3 right!? QUERY
+# Based on this, they expected to detect a 2mmHg drop with 85% power and n = 82
+
+# inclusion: Systolic blood pressure: 130 – 149 mmHg
+
+# 2 week pre-trial run-in (advised to not eat berries)
+
+# Block randomized....do I have block info? QUERY
+
+  names(data) <- tolower(names(data))
+
+# Save labels from Haven
+
+  label.list <- list()
+
+  for (i in seq_along(data)){
+    label.list[[i]] <- attributes(data[[i]])$label
+  }
+
+# Remove labelled class
+
+  data <- unlabel(data)
+
+# Remove NaNs
+
+  data[sapply(data, is.numeric)] <- apply(data[sapply(data, is.numeric)], 2,
+                                          function(x) ifelse(is.nan(x), NA, x))
+
+# Fix inconsistent naming
+
+  stub_change <- function(stub, ...){
+    x <- gsub(paste0("_", stub), "", names(data)[grepl(stub, names(data))]) %>%
+      paste0(paste0(stub, "_"), .)
+    return(x)
+  }
+
+  names(data)[grepl("tag", names(data))]   <- stub_change("tag")
+  names(data)[grepl("hdl", names(data))]   <- stub_change("hdl")
+  names(data)[grepl("tchol", names(data))] <- stub_change("tchol")
+
+  names(data)[grepl("_ldl", names(data))] <-
+    gsub("_ldl", "", names(data)[grepl("_ldl", names(data))]) %>%
+    paste0("ldl_", .)
+
+  names(data) <- gsub("p_1", "p1", names(data)) %>%
+    gsub("p_2", "p2", .) %>%
+    gsub("_bl_", "_b_", .)
+
+  save(data, file = "trial_data_july_2019.RData")
+
+
+
+
+
+

### 2019-12-31 scripts/04_primary_outcome.R

@@ -1,0 +1,309 @@
+
+  library(tidyverse)
+  source("scripts/functions.R")
+  load("trial_data_july_2019.RData") # See scripts/data.R
+
+# Primary outcome --------------------------------------------------------------
+
+# SBP --------------------------------------------------------------------------
+
+# Reshape the data on 4 SBP values in order to plot the within period changes
+# by tx group, get missing values. See functions.R
+
+  sbp <- outcomes(data, "sbp__")
+
+# Missing values
+  length(data$subj_id); table(is.na(data$subj_id)) # 83
+  length(data$sequence); table(is.na(data$sequence)) # 83
+
+  group_by(sbp, period, timing, tx) %>%
+    summarise(sbp_missings = sum(is.na(value))) %>%
+    filter(sbp_missings > 0) # 4 total values
+
+# Distribution plot
+
+  dist(sbp, "SBP (mmHg)")
+
+  ggsave("plots/primary/sbp_dist2.pdf", width = 33.867, height = 19.05, units = "cm",
+         scale = 0.6, dpi = 600)
+
+# Cross over plot
+
+  cross_plot(sbp, "SBP (mmHg)")
+
+  ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
+         scale = 0.6, dpi = 600)
+
+# Models
+
+  me_sbp_df <- full_join(
+    select(sbp, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
+    select(sbp, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
+    by = c("subj_id", "period", "tx", "sex")
+  ) %>%
+    mutate(bl = scale(bl, scale = FALSE))
+
+  library(lme4)
+
+  me_sbp     <- lmer(ep ~ tx + sex +               (1 | subj_id),
+                     data = me_sbp_df)
+  me_sbp_p   <- lmer(ep ~ tx + sex + period +      (1 | subj_id),
+                     data = me_sbp_df)
+  me_sbp_int <- lmer(ep ~ tx * period +  sex +     (1 | subj_id),
+                     data = me_sbp_df)
+  me_sbp_bl  <- lmer(ep ~ tx + sex + period + bl + (1 | subj_id),
[…]

### 2019-12-31 scripts/05_secondary_outcomes.R

@@ -1,0 +1,522 @@
+# Secondary objectives
+
+# DBP ####
+
+  dbp <- outcomes(data, "dbp__")
+
+  group_by(dbp, period, timing, tx) %>%
+    summarise(dbp_missings = sum(is.na(value))) %>%
+    filter(dbp_missings > 0) # 4 total values
+
+# Distribution plot
+
+  dist(dbp, "DBP (mmHg)", logged = "no")
+
+  ggsave("plots/secondary/dbp_dist2.pdf", width = 33.867, height = 19.05, units = "cm",
+         scale = 0.6, dpi = 600)
+
+# Cross over plot #
+
+  cross_plot(dbp, "DBP (mmHg)", logged = "no")
+
+  ggsave("plots/secondary/dbp.pdf", width = 33.867, height = 19.05, units = "cm",
+         scale = 0.6, dpi = 600)
+
+# Models #
+
+  me_dbp_df <- full_join(
+    select(dbp, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
+    select(dbp, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
+    by = c("subj_id", "period", "tx", "sex")
+  ) %>%
+    mutate(bl = scale(bl, scale = FALSE))
+
+  library(lme4)
+
+  me_dbp     <- lmer(ep ~ tx + sex +               (1 | subj_id),
+                     data = me_dbp_df)
+  me_dbp_p   <- lmer(ep ~ tx + sex + period +      (1 | subj_id),
+                     data = me_dbp_df)
+  me_dbp_int <- lmer(ep ~ tx * period +  sex +     (1 | subj_id),
+                     data = me_dbp_df)
+  me_dbp_bl  <- lmer(ep ~ tx + sex + period + bl + (1 | subj_id),
+                     data = me_dbp_df)
+
+  library(sjPlot)
+
+  labs <- c("Intercept", "Treatment", "Sex", "Period")
+
+  tab_model(
+    me_dbp, me_dbp_p, me_dbp_bl,
+    p.val = "kr",
+    file = "tables/secondary/table_me_dbp.html",
+    pred.labels = c(labs, "DBP Baseline"),
+    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
+   )
+
+# OXLDL ####
+
+  oxldl <- outcomes(data, "oxldl_")
+
+  group_by(oxldl, period, timing, tx) %>%
[…]

### 2019-12-31 scripts/06_other_models.R

@@ -1,0 +1,11 @@
+# Other tests
+
+# Paired-t-test
+
+# Different contrasts
+
+  c1 <- c(0.5, -0.5)
+
+  model <- lmer(out ~ 1 + sequence + (1|subj:sequence) + period + tx,
+                contrasts = list(sequence = c1, Period = c1, tx = c1),
+                data  == data)

### 2019-12-31 paper_stats.Rmd
update analysis

@@
     df_print: paged
+    keep_md: true
 ---
@@
 
-  load("scripts/models_dec_2019.RData")
+# load("scripts/models_dec_2019.RData")
+  source("scripts/01_project.R") # Produces the model and data objects
 
@@
              ll = signif(estimate - (1.96 * std.error), 3)) %>%
-      filter(term == "tx2")
+      filter(term == "txActive")
 
@@
     select(data, subj_id, tx, ep) %>% 
-    mutate(tx = factor(tx, labels = c("Control", "Active"))) %>%
     spread(tx, ep) %>% 
@@
   get_p <- function(model){
-    x <- sjstats::p_value(model) %>% filter(term == "tx2")
+    x <- sjstats::p_value(model) %>% filter(term == "txActive")
     return(signif(x$p.value, 2))
@@
              var = varname) %>%
-      filter(term == "tx2")
+      filter(term == "txActive")
 
@@
 
-    ggsave("plots/primary/all.pdf", width = 33.867, height = 19.05, units = "cm",
-         scale = 0.6, dpi = 600)
+# ggsave("plots/primary/all.pdf", width = 33.867, height = 19.05, units = "cm",
+#      scale = 0.6, dpi = 600)
 
@@
 
-  ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
-         scale = 0.6, dpi = 600)
+# ggsave("plots/primary/sbp.pdf", width = 33.867, height = 19.05, units = "cm",
+#        scale = 0.6, dpi = 600)
 ```
@@
 
-  var_ratio <- function(df, var_lab, logged, ...){
+  var_ratio <- function(df, var_lab, logged = "No", ...){
 
@@
 
-  var_ratio(sbp, "SBP")
+# var_ratio(sbp, "SBP")
 
@@
 
-  dist(sbp, "SBP (mmHg)") +
-    ggtitle("Systolic Blood Pressure")
-
-  dist(dbp, "DBP (mmHg)", logged = "no") +
-    ggtitle("Diastolic Blood Pressure")
-
-  dist(oxldl, "Log(OXLDL)", logged = "yes") +
-    ggtitle("OXDL")
-
-  dist(art_stif, "Arterial Stiffness", logged = "no")+
-    ggtitle("Arterial Stiffness")
-
-  dist(glu, "Glucose", logged = "no") +
-    ggtitle("Glucose")
-
-  dist(ldl, "LDL", logged = "no") +
-    ggtitle("LDL")
-
-  dist(hdl, "Log(HDL)", logged = "yes") +
-    ggtitle("HDL")
-
-  dist(tchol, "Log(TCHOL)", logged = "yes")+
-    ggtitle("Total cholesterol")
-
-  dist(tag, "Log(TAG)", logged = "yes")+
-    ggtitle("TAG")
-
-  dist(pwa_augment, "PWA Augment", logged = "no")+
-    ggtitle("Diastolic Blood Pressure")
+  # dist(sbp, "SBP (mmHg)") +
+  #   ggtitle("Systolic Blood Pressure")
+  # 
+  # dist(dbp, "DBP (mmHg)", logged = "no") +
+  #   ggtitle("Diastolic Blood Pressure")
+  # 
+  # dist(oxldl, "Log(OXLDL)", logged = "yes") +
+  #   ggtitle("OXDL")
+  # 
+  # dist(art_stif, "Arterial Stiffness", logged = "no")+
+  #   ggtitle("Arterial Stiffness")
+  # 
+  # dist(glu, "Glucose", logged = "no") +
+  #   ggtitle("Glucose")
+  # 
+  # dist(ldl, "LDL", logged = "no") +
+  #   ggtitle("LDL")
+  # 
+  # dist(hdl, "Log(HDL)", logged = "yes") +
+  #   ggtitle("HDL")
+  # 
+  # dist(tchol, "Log(TCHOL)", logged = "yes")+
+  #   ggtitle("Total cholesterol")
+  # 
+  # dist(tag, "Log(TAG)", logged = "yes")+
+  #   ggtitle("TAG")
+  # 
+  # dist(pwa_augment, "PWA Augment", logged = "no")+
+  #   ggtitle("Diastolic Blood Pressure")
+  #
 

### 2019-12-31 scripts/01_project.R

@@ -1,14 +1,13 @@
 
+  source("scripts/02_functions.R")
 
-  source("scripts/functions.R")
+  source("scripts/03_data.R")
 
-  source("scripts/data.R")
+  source("scripts/04_primary_outcome.R")
 
-  source("scripts/primary_outcome.R")
+  source("scripts/05_secondary_outcomes.R")
 
-  source("scripts/secondary_outcomes.R")
-
-  save.image(file = "scripts/models_dec_2019.RData")
+# save.image(file = gsub(" ", "_", paste0("data_models_", date(), ".RData")))
 
 
 

### 2019-12-31 scripts/03_data.R

@@ -1,6 +1,5 @@
 
   library(tidyverse)
-  source("scripts/functions.R")
 
 # Data -------------------------------------------------------------------------
 
@@ -57,7 +56,7 @@
     gsub("p_2", "p2", .) %>%
     gsub("_bl_", "_b_", .)
 
-  save(data, file = "trial_data_july_2019.RData")
+# save(data, file = gsub(" ", "_", paste0("data_", date(), ".RData")))
 
 
 

### 2019-12-31 scripts/04_primary_outcome.R

@@ -1,40 +1,45 @@
 
   library(tidyverse)
-  source("scripts/functions.R")
-  load("trial_data_july_2019.RData") # See scripts/data.R
+  library(lme4)
+  library(sjPlot)
 
-# Primary outcome --------------------------------------------------------------
+# Primary outcomes were noted as:
+# Paper:    Office and central BPs
+# Protocol: Not specified, but notes impact on SBP as primary objective (protocol)
+# Registry: "Blood Pressure [ Time Frame: 42 days ] A change between baseline
+# blood pressure and endpoint blood pressure within the intervention group versus
+# # the control group." (https://clinicaltrials.gov/ct2/show/NCT02355444)
 
 # SBP --------------------------------------------------------------------------
 
 # Reshape the data on 4 SBP values in order to plot the within period changes
-# by tx group, get missing values. See functions.R
+# by tx group, get missing values. See 02_functions.R
 
   sbp <- outcomes(data, "sbp__")
 
 # Missing values
-  length(data$subj_id); table(is.na(data$subj_id)) # 83
-  length(data$sequence); table(is.na(data$sequence)) # 83
+# length(data$subj_id); table(is.na(data$subj_id)) # 83
+# length(data$sequence); table(is.na(data$sequence)) # 83
+#
+# group_by(sbp, period, timing, tx) %>%
+#   summarise(sbp_missings = sum(is.na(value))) %>%
+#   filter(sbp_missings > 0) # 4 total values
 
-  group_by(sbp, period, timing, tx) %>%
-    summarise(sbp_missings = sum(is.na(value))) %>%
-    filter(sbp_missings > 0) # 4 total values
+# Distribution plot ####
 
-# Distribution plot
+# dist(sbp, "SBP (mmHg)") # See 02_functions.R
+#
+# ggsave("plots/primary/sbp_dist2.pdf", width = 33.867, height = 19.05, units = "cm",
+#        scale = 0.6, dpi = 600)
 
-  dist(sbp, "SBP (mmHg)")
+# Cross over plot ####
 
[…]

### 2019-12-31 scripts/05_secondary_outcomes.R

@@ -1,92 +1,137 @@
-# Secondary objectives
 
-# DBP ####
+  library(tidyverse)
+  library(lme4)
+  library(sjPlot)
 
-  dbp <- outcomes(data, "dbp__")
+# OCS SBP ----------------------------------------------------------------------
 
-  group_by(dbp, period, timing, tx) %>%
-    summarise(dbp_missings = sum(is.na(value))) %>%
-    filter(dbp_missings > 0) # 4 total values
+  osc_sbp <- outcomes(data, "osc_sbp__")
 
-# Distribution plot
+# group_by(osc_sbp, period, timing, tx) %>%
+#   summarise(osc_sbp_missings = sum(is.na(value))) %>%
+#   filter(osc_sbp_missings > 0) # 4 total values
 
-  dist(dbp, "DBP (mmHg)", logged = "no")
+# Distribution plot ####
 
-  ggsave("plots/secondary/dbp_dist2.pdf", width = 33.867, height = 19.05, units = "cm",
-         scale = 0.6, dpi = 600)
+# dist(osc_sbp, "OSC SBP (mmHg)", logged = "no")
+#
+# ggsave("plots/primary/osc_sbp_dist2.pdf", width = 33.867, height = 19.05, units = "cm",
+#        scale = 0.6, dpi = 600)
 
-# Cross over plot #
+# Cross over plot ####
 
-  cross_plot(dbp, "DBP (mmHg)", logged = "no")
+# cross_plot(osc_sbp, "OSC SBP (mmHg)", logged = "no")
+#
+# ggsave("plots/primary/osc_sbp.pdf", width = 33.867, height = 19.05, units = "cm",
+#        scale = 0.6, dpi = 600)
 
-  ggsave("plots/secondary/dbp.pdf", width = 33.867, height = 19.05, units = "cm",
-         scale = 0.6, dpi = 600)
+# Models ####
 
-# Models #
-
-  me_dbp_df <- full_join(
-    select(dbp, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
-    select(dbp, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
+  me_osc_sbp_df <- full_join(
+    select(osc_sbp, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
+    select(osc_sbp, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
     by = c("subj_id", "period", "tx", "sex")
   ) %>%
[…]

### 2019-12-31 paper_stats.Rmd
knit html
update analysis

@@
 output:
-  word_document:
-    reference_docx: style.1.docx
   html_document:
@@
     keep_md: true
+  word_document:
+    reference_docx: style.1.docx
 ---
@@
   library(broom)
+  library(pander)
 
@@
              "Median [IQR]" = med.iqr(descript),
-             "(Min, Max)"   = min.max(descript)) %>% knitr::kable()
+             "(Min, Max)"   = min.max(descript)) %>% 
+  pander()
 
@@
 
-  knitr::kable(table_df)
+  pander(table_df)
 
@@
       mutate(ep = log(ep)) %>%
-            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
       filter(!is.na(ep)) %>%
@@
     data <- select(df, subj_id, tx, ep) %>% 
-            mutate(tx = factor(tx, labels = c("Control", "Active"))) %>% 
       filter(!is.na(ep)) %>%
@@
 
-    data <- data_frame(var = var_lab, 
+    data <- data_frame(
+      var = var_lab, 
       vr = signif(sdx^2/sdy^2, 2), 
-                       p = round(p, 3))
+      p = round(p, 3)
+      )
 
@@
 
-  vrs_df <- do.call(bind_rows, map2(data_list, varnames,  var_ratio))
+  df <- data.frame(
+    df = I(list(sbp, dbp, c_sbp, c_dbp, art_stif, glu, hdl, ldl, oxldl,
+                pwa_augment, tag, tchol)),
+    var_lab = c("SBP", "DBP", "Central SBP", "Central DBP", 
+                "Arterial Stiffness", "Glucose", "log(HDL)", "LDL", "log(OxLDL)", 
+                "PWA Augment", "log(TAG)", "log(Total Cholesterol)"), 
+    logged = c(rep("No", 6), "Yes", "No", "Yes", "No", "Yes", "Yes"),
+    stringsAsFactors = FALSE
+    )
 
-  vrs_df
+  vrs_df <- do.call(bind_rows, pmap(df, var_ratio))
+
+  pander(vrs_df)
 
@@
 
-  # dist(sbp, "SBP (mmHg)") +
-  #   ggtitle("Systolic Blood Pressure")
-  # 
-  # dist(dbp, "DBP (mmHg)", logged = "no") +
-  #   ggtitle("Diastolic Blood Pressure")
-  # 
-  # dist(oxldl, "Log(OXLDL)", logged = "yes") +
-  #   ggtitle("OXDL")
-  # 
-  # dist(art_stif, "Arterial Stiffness", logged = "no")+
-  #   ggtitle("Arterial Stiffness")
-  # 
-  # dist(glu, "Glucose", logged = "no") +
-  #   ggtitle("Glucose")
-  # 
-  # dist(ldl, "LDL", logged = "no") +
-  #   ggtitle("LDL")
-  # 
-  # dist(hdl, "Log(HDL)", logged = "yes") +
-  #   ggtitle("HDL")
-  # 
-  # dist(tchol, "Log(TCHOL)", logged = "yes")+
-  #   ggtitle("Total cholesterol")
-  # 
-  # dist(tag, "Log(TAG)", logged = "yes")+
-  #   ggtitle("TAG")
-  # 
-  # dist(pwa_augment, "PWA Augment", logged = "no")+
-  #   ggtitle("Diastolic Blood Pressure")
-  #
+  dist(sbp, "SBP (mmHg)", logged = "no")
+
+  dist(dbp, "DBP (mmHg)", logged = "no")
+
+  dist(art_stif, "Arterial Stiffness", logged = "no")
+
+  dist(glu, "Glucose", logged = "no")
+
+  dist(hdl, "HDL", logged = "no")
+  dist(hdl, "Log(HDL)", logged = "yes")
+
+  dist(ldl, "LDL", logged = "no")
+
+  dist(oxldl, "OXLDL", logged = "no")
+  dist(oxldl, "Log(OXLDL)", logged = "yes")
+
+  dist(pwa_augment, "PWA Augment", logged = "no")
+
+  dist(tag, "TAG", logged = "no")
+  dist(tag, "Log(TAG)", logged = "yes")
+
+  dist(tchol, "TCHOL", logged = "no")
+  dist(tchol, "Log(TCHOL)", logged = "yes")
 

### 2019-12-31 paper_stats.Rmd
change tables

@@
   library(broom)
-  library(pander)
+  library(knitr)
 
@@
              "(Min, Max)"   = min.max(descript)) %>% 
-  pander()
+  kable()
 
@@
 
-  pander(table_df)
+  kable(table_df)
 
@@
 
-  pander(vrs_df)
+  kable(vrs_df)
 

### 2019-12-31 paper_stats.Rmd
update
tables

@@
              "Median [IQR]" = med.iqr(descript),
-             "(Min, Max)"   = min.max(descript)) %>% 
-  kable()
+             "(Min, Max)"   = min.max(descript))
 

### 2019-12-31 paper_stats.Rmd
tables

@@
   library(knitr)
+  library(pander)
 
@@
              "Median [IQR]" = med.iqr(descript),
-             "(Min, Max)"   = min.max(descript))
+             "(Min, Max)"   = min.max(descript)) %>%
+  as.matrix() %>%
+  kable()
 
@@
 
-  table_df <- full_join(means_df, difs_df, by = "Outcome") %>%
-    select(Outcome, everything())
-
-  kable(table_df)
+  full_join(means_df, difs_df, by = "Outcome") %>%
+    select(Outcome, everything()) %>%
+    as.matrix() %>%
+    pander()
 

### 2019-12-31 paper_stats.Rmd
tables

@@
   as.matrix() %>%
+  as.table() %>%
   kable()
@@
     as.matrix() %>%
+    as.table() %>%
     pander()

### 2019-12-31 paper_stats.Rmd
tables

--- 2019-12-31 paper_stats.Rmd
@@
 
-```{r table1_describe}
+```{r table1_describe, results = "asis"}
 
@@
              "(Min, Max)"   = min.max(descript)) %>%
-  as.matrix() %>%
   kable()
@@
 Table 2. Blood pressure outcomes
-```{r}
+```{r results = "asis"}
 
@@
     select(Outcome, everything()) %>%
-    as.matrix() %>%
     pander()

### 2019-12-31 paper_stats.Rmd
tables

@@
   library(pander)
+  library(DT)
 
@@
 Table 1. Respondent characteristics
+
 ```{r table1_data}
@@
              "(Min, Max)"   = min.max(descript)) %>%
-  kable()
+  datatable()
 
@@
 Table 2. Blood pressure outcomes
+
 ```{r results = "asis"}
@@
 Figure 1. Mixed-effect model estimated treatment effects for blood pressure outcomes.
+
 ```{r}
@@
 Figure 2. Change in systolic blood pressure across the two study periods
+
 ```{r}

### 2019-12-31 paper_stats.Rmd
tables
table

@@
 
-```{r table1_describe, results = "asis"}
+```{r table1_describe}
 
@@
              "(Min, Max)"   = min.max(descript)) %>%
-  datatable()
+  kable()
 
@@
 
-```{r results = "asis"}
+```{r}
 
@@
     select(Outcome, everything()) %>%
-    pander()
+    kable()
 

### 2019-12-31 paper_stats.Rmd
tables

@@
   library(knitr)
-  library(pander)
-  library(DT)
+  library(xtable)
 
@@
              "(Min, Max)"   = min.max(descript)) %>%
-  kable()
+  xtable()
 

### 2020-01-01 paper_stats.Rmd
tables

@@
   library(knitr)
-  library(xtable)
+  library(flextable)
 
@@
              "(Min, Max)"   = min.max(descript)) %>%
-  xtable()
+  flextable()
 
@@
     select(Outcome, everything()) %>%
-    kable()
+    flextable()
 
@@
 
-  vrs_df <- do.call(bind_rows, pmap(df, var_ratio))
-
-  kable(vrs_df)
+  do.call(bind_rows, pmap(df, var_ratio)) %>%
+    flextable()
 

### 2020-01-01 paper_stats.Rmd
big update

@@
 ```
-
-```{r hdl_variance_plot}
-
-  mutate(hdl, tx = factor(tx, labels = c("Control", "Active"))) %>%
-  filter(!is.na(ep)) %>%
-  ggplot(aes(x = log(ep), fill = tx)) +
-    geom_density(alpha = 0.5, color = "black") +
-    theme_minimal() +
-    xlab("HDL") +
-    ylab("Density") +
-    scale_fill_brewer("", palette = "Set1")
-
-```
-
-```{r all_distributions}
-
-  dist(sbp, "SBP (mmHg)", logged = "no")
-
-  dist(dbp, "DBP (mmHg)", logged = "no")
-
-  dist(art_stif, "Arterial Stiffness", logged = "no")
-
-  dist(glu, "Glucose", logged = "no")
-
-  dist(hdl, "HDL", logged = "no")
-  dist(hdl, "Log(HDL)", logged = "yes")
-
-  dist(ldl, "LDL", logged = "no")
-
-  dist(oxldl, "OXLDL", logged = "no")
-  dist(oxldl, "Log(OXLDL)", logged = "yes")
-
-  dist(pwa_augment, "PWA Augment", logged = "no")
-
-  dist(tag, "TAG", logged = "no")
-  dist(tag, "Log(TAG)", logged = "yes")
-
-  dist(tchol, "TCHOL", logged = "no")
-  dist(tchol, "Log(TCHOL)", logged = "yes")
-
-```

### 2020-01-01 supplement.Rmd
big update

@@
 ---
-title: "supplmental"
-output: html_document
+title: ''
+author: ''
+date: ''
+output: 
+  html_document:
+    df_print: paged
+    keep_md: true
+  word_document:
+    reference_docx: style.1.docx
 ---
@@
 
-  library(tidyverse)
-  source("scripts/functions.R")
-  load("scripts/models_july_2019.RData")
+# load("scripts/models_dec_2019.RData")
+  source("scripts/01_project.R") # Produces the model and data objects
 
   library(sjPlot)
+  library(tidyverse)
 
@@
 
-Table 3. Mixed-effects model estimates for systolic blood pressure (mmHg)
+Mixed-effects model estimates for systolic blood pressure (mmHg)
 
@@
 
-S-Table 1. Mixed-effects model estimates for diastolic blood pressure (mmHg)
+Mixed-effects model estimates for diastolic blood pressure (mmHg)
 
@@
 
-S-Table 2. Mixed-effects model estimates for oscillatory systolic blood pressure (mmHg)
-```{r}
-
-# OCS SBP
-
-  tab_model(
-    me_osc_sbp, me_osc_sbp_p, me_osc_sbp_bl,
-    p.val = "kr",
-    file = "tables/primary/table_me_osc_sbp.html",
-    pred.labels = c(labs, "OSC SBP Baseline"),
-    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
-    )
-
-```
-
-S-Table 3. Mixed-effects model estimates for oscillatory diastolic blood pressure (mmHg)
-
-```{r}
-
-# OCS DBP
-
-  tab_model(
-    me_osc_dbp, me_osc_dbp_p, me_osc_dbp_bl,
-    p.val = "kr",
-    file = "tables/primary/table_me_osc_dbp.html",
-    pred.labels = c(labs, "OSC DBP Baseline"),
-    dv.labels = c("Unadjusted", "+ Period effect", "+ Baselines")
-    )
-
-```
-
-S-Table 4. Mixed-effects model estimates for central systolic blood pressure (mmHg)
+Mixed-effects model estimates for central systolic blood pressure (mmHg)
 
@@
 
-S-Table 5. Mixed-effects model estimates for central diastolic blood pressure (mmHg)
+Mixed-effects model estimates for central diastolic blood pressure (mmHg)
 
@@
 
-S-Table 6. Mixed-effects model estimates for OXLDL
+Mixed-effects model estimates for log(OXLDL)
 
 ```{r}
+
 # OXLDL ####
@@
 
-S-Table 7. Mixed-effects model estimates for arterial stiffness
+Mixed-effects model estimates for arterial stiffness
 
@@
 
-S-Table 8. Mixed-effects model estimates for fasting glucose
+Mixed-effects model estimates for fasting glucose
 
@@
 
-S-Table 9. Mixed-effects model estimates for LDL
+Mixed-effects model estimates for LDL
 
@@
 
-S-Table 10. Mixed-effects model estimates for HDL
+Mixed-effects model estimates for log(HDL)
 
@@
 
-S-Table 11. Mixed-effects model estimates for total cholesterol
+Mixed-effects model estimates for log(total cholesterol)
 
@@
 
-S-Table 12. Mixed-effects model estimates for TAG
+Mixed-effects model estimates for log(TAG)
 
@@
 
-S-Table 13. Mixed-effects model estimates for PWA augment
+Mixed-effects model estimates for PWA augment
 
@@
 ```
+
+```{r hdl_variance_plot}
+
+  mutate(hdl, tx = factor(tx, labels = c("Control", "Active"))) %>%
+  filter(!is.na(ep)) %>%
+  ggplot(aes(x = log(ep), fill = tx)) +
+    geom_density(alpha = 0.5, color = "black") +
+    theme_minimal() +
+    xlab("HDL") +
+    ylab("Density") +
+    scale_fill_brewer("", palette = "Set1")
+
+```
+
+```{r all_distributions}
+
+  dist(sbp, "SBP (mmHg)", logged = "no")
+
+  dist(dbp, "DBP (mmHg)", logged = "no")
+
+  dist(art_stif, "Arterial Stiffness", logged = "no")
+
+  dist(glu, "Glucose", logged = "no")
+
+  dist(hdl, "HDL", logged = "no")
+  dist(hdl, "Log(HDL)", logged = "yes")
+
+  dist(ldl, "LDL", logged = "no")
+
+  dist(oxldl, "OXLDL", logged = "no")
+  dist(oxldl, "Log(OXLDL)", logged = "yes")
+
+  dist(pwa_augment, "PWA Augment", logged = "no")
+
+  dist(tag, "TAG", logged = "no")
+  dist(tag, "Log(TAG)", logged = "yes")
+
+  dist(tchol, "TCHOL", logged = "no")
+  dist(tchol, "Log(TCHOL)", logged = "yes")
+
+```

### 2020-01-01 scripts/02_functions.R

@@ -72,10 +72,8 @@
                       group = treatment_p2),
                   se = FALSE, size = 2) +
       scale_linetype(guide = FALSE) +
-      theme_minimal() +
       scale_color_brewer("Tx", palette = "Set1") +
-      theme(panel.grid.major = element_blank(),
-            panel.grid.minor = element_blank()) +
+      theme(panel.grid.major = element_blank()) +
       scale_x_discrete(labels = c("Start P1", "End P1", "Start P2", "End P2")) +
       xlab("") +
       ylab(ylabel))
@@ -98,10 +96,8 @@
                         group = treatment_p2),
                     se = FALSE, size = 2) +
         scale_linetype(guide = FALSE) +
-        theme_minimal() +
         scale_color_brewer("Tx", palette = "Set1") +
-        theme(panel.grid.major = element_blank(),
-              panel.grid.minor = element_blank()) +
+        theme(panel.grid.major = element_blank()) +
         scale_x_discrete(labels = c("Start P1", "End P1", "Start P2", "End P2")) +
         xlab("") +
         ylab(ylabel))
@@ -122,9 +118,7 @@
       scale_fill_brewer("Tx", palette = "Set1") +
       scale_color_brewer("Tx", palette = "Set1") +
       facet_wrap(~period + timing) +
-      theme_minimal() +
-      theme(panel.grid.major = element_blank(),
-            panel.grid.minor = element_blank()) +
+      theme(panel.grid.major = element_blank()) +
       ylab("") +
       xlab(ylabel))
     }
@@ -137,9 +131,7 @@
         scale_fill_brewer("Tx", palette = "Set1") +
         scale_color_brewer("Tx", palette = "Set1") +
         facet_wrap(~period + timing) +
-        theme_minimal() +
-        theme(panel.grid.major = element_blank(),
-              panel.grid.minor = element_blank()) +
+        theme(panel.grid.major = element_blank()) +
         ylab("") +
         xlab(ylabel))
     }

### 2020-01-01 scripts/05_secondary_outcomes.R

@@ -138,6 +138,7 @@
     select(oxldl, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
     by = c("subj_id", "period", "tx", "sex")
   ) %>%
+    mutate(bl = log(bl), ep = log(ep)) %>%
     mutate(bl = scale(bl, scale = FALSE))
 
   me_oxldl     <- lmer(ep ~ tx + sex +               (1 | subj_id),
@@ -370,7 +371,9 @@
   me_hdl_df <- full_join(
     select(hdl, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
     select(hdl, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
-    by = c("subj_id", "period", "tx", "sex")) %>%
+    by = c("subj_id", "period", "tx", "sex")
+    ) %>%
+    mutate(bl = log(bl), ep = log(ep)) %>%
     mutate(bl = scale(bl, scale = FALSE))
 
   me_hdl     <- lmer(ep ~ tx + sex +               (1 | subj_id),
@@ -428,7 +431,9 @@
   me_tchol_df <- full_join(
     select(tchol, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
     select(tchol, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
-    by = c("subj_id", "period", "tx", "sex")) %>%
+    by = c("subj_id", "period", "tx", "sex")
+    ) %>%
+    mutate(bl = log(bl), ep = log(ep)) %>%
     mutate(bl = scale(bl, scale = FALSE))
 
   me_tchol     <- lmer(ep ~ tx + sex +               (1 | subj_id),
@@ -485,7 +490,9 @@
   me_tag_df <- full_join(
     select(tag, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),
     select(tag, subj_id, sex, period, ep, tx) %>% filter(!is.na(ep)),
-    by = c("subj_id", "period", "tx", "sex")) %>%
+    by = c("subj_id", "period", "tx", "sex")
+    ) %>%
+    mutate(bl = log(bl), ep = log(ep)) %>%
     mutate(bl = scale(bl, scale = FALSE))
 
   me_tag     <- lmer(ep ~ tx + sex +               (1 | subj_id),

### 2020-01-05 paper_stats.Rmd
update

@@
 output: 
+  word_document:
+    reference_docx: style.1.docx
   html_document:
@@
     keep_md: true
-  word_document:
-    reference_docx: style.1.docx
 ---
@@
 Continuous variables were described by their means and SDs, medians and IQRs, and their range; while categorical variables were described by their counts and percentages in each category.
-Average treatment effects were estimated using mixed effects models with a random effect for participant.
+
+Average treatment effects were estimated using multilevel models with a random effect for participant.
 All reported models were adjusted for the sex of the participant (to correspond to the sex-stratified randomization lists).
@@
 We did not apply any adjustment for multiple testing, but have provided enough information for the reader to do so it they wish.
-Data were analysed on an intent-to-treat basis (i.e.
-without consideration for intervention compliance).
+Data were analysed on an intent-to-treat basis.
 
-To evalaute the possilbity of heterogeneity of treatment effects, we
+Senn REF: 
+Cross-over Trials in Clinical Research. Stephen Senn. Second Edition: Published August 2002 ISBN 0 471 49653 7
+
+KR REF:
+Ulrich Halekoh, Søren Højsgaard (2014)., A Kenward-Roger Approximation and Parametric Bootstrap
+Methods for Tests in Linear Mixed Models - The R Package pbkrtest., Journal of Statistical
+Software, 58(10), 1-30., http://www.jstatsoft.org/v59/i09/
+
+To evalaute the possilbity of heterogeneity of treatment effects, we followed the advice of Cortes et al.
+(REF) and calulated the various outcome variances for the baseline and end-of-period values under the active treatment condtion, and tested wheher the resulting outcome-specific variance ratios were equal to 1 using a two-sided Pitman Morgan test for paired observations (REF).
+We reported exact p-values from this test.
+
+Cortes REF: 
+Cortés J, González JA, Medina MN et al.
+Does evidence support the high expectations placed in precision medicine?
+A bibliographic review [version 5; peer review: 2 approved, 1 approved with reservations, 3 not approved].
+F1000Research 2019, 7:30 (https://doi.org/10.12688/f1000research.13490.5)
+
+Pitman-Morgan REFs:
+Sachs L: Applied Statistics: A Handbook of Techniques. 2nd ed. New York: Springer-Verlag, 1984.
+
+Morgan, W.A. (1939) A test for the significance of the difference between two variances in a sample from a normal bivariate distribution. Biometrika, 31, 13-19.
 
@@
 We used the lme4 package (REF) to estimate mixed effects models; ggplot2 (REF) to generate plots; and sjPlot to produce tables of model results.
-All anonymized data and the code used to analyze it and generate outputs can be found on the Open Science Framework (https://osf.io/zq4y9/).
+All anonymized data and the code used for the analysis and to generate outputs can be found on the Open Science Framework (https://osf.io/zq4y9/).
 
@@
 
-```{r table1_describe}
+```{r table1_describe_html, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
 
-  data_frame(Variable       = name.1(descript),
+  data_frame(Variable       = tools::toTitleCase(gsub("_", " ", name.1(descript))),
              N              = n.miss(descript),
@@
   flextable()
+
+```
+
+```{r table1_describe_word, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
+
+  data_frame(Variable       = tools::toTitleCase(gsub("_", " ", name.1(descript))),
+             N              = n.miss(descript),
+             "Mean SD"      = summary.1(descript),
+             "Median [IQR]" = med.iqr(descript),
+             "(Min, Max)"   = min.max(descript)) %>%
+  kable()
 
@@
     filter(!is.na(effect)) %>%
-    summarise(Mean_diff = signif(mean(effect, na.rm = TRUE), 2),
-              SD_diff = signif(sd(effect, na.rm = TRUE), 2), 
-              n_diff = n(), 
+    summarise(n_diff = n(), 
+              Difference = paste0(
+                signif(mean(effect, na.rm = TRUE), 2),
+                " (",
+                signif(sd(effect, na.rm = TRUE), 2),
+                ")"
+              ),
               Outcome = var) %>% 
-    select(Outcome, n_diff, Mean_diff, SD_diff) %>%
+    select(Outcome, n_diff, Difference) %>%
     return()
@@
         summarise(n_control = n(), 
-                  mean_control = signif(mean(ep, na.rm = TRUE), 2), 
-                  sd_control = signif(sd(ep, na.rm = TRUE), 2), 
+                  Control = paste0(
+                    signif(mean(ep, na.rm = TRUE), 2),
+                    " (",
+                    signif(sd(ep, na.rm = TRUE), 2),
+                    ")"
+                    ),
                   Outcome = var), 
@@
         summarise(n_active = n(), 
-                  mean_active = signif(mean(ep, na.rm = TRUE), 2), 
-                  sd_active = signif(sd(ep, na.rm = TRUE), 2), 
+                  Active = paste0(
+                    signif(mean(ep, na.rm = TRUE), 2),
+                    " (",
+                    signif(sd(ep, na.rm = TRUE), 2),
+                    ")"
+                    ),
                   Outcome = var), 
@@
   means_df <- do.call(bind_rows, map2(data_list, varnames, means_sds))
+
+```
+
+```{r table2_outcomes_word, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
+
+  full_join(means_df, difs_df, by = "Outcome") %>%
+    select(Outcome, everything()) %>%
+    knitr::kable()
+
+```
+
+```{r table2_outcomes_html, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
 
@@
 
-```{r}
+```{r active_vs_control_diff, eval = FALSE}
+
+# This calculates, for each patient, the variance of the outcome at the end of 
+# period under control, and the same variance under active. These values are 
+# paired, so a paired test is used on the resulting variance ratio.
 
 # https://zenodo.org/record/1239539 code
+# The specific test can be found in Sachs p 311
+# https://books.google.ie/books?id=A0bhBwAAQBAJ&printsec=frontcover&dq=Applied+Statistics+A+Handbook+of+Techniques&hl=en&sa=X&ved=0ahUKEwimxdfHxufmAhWsTBUIHbcoBOYQ6AEIKTAA#v=onepage&q=paired&f=false
 
@@
 ```
+
+```{r bl_vs_ep_diff_in_treated}
+
+# This calculates, for each patient, the variance of the outcome at the end of 
+# period under active, and the same variance for the baseline under active. 
+# These values are paired, so a paired test is used on the resulting variance 
+# ratio.
+
+# https://zenodo.org/record/1239539 code
+
+  var_ratio <- function(df, var_lab, logged = "No", ...){
+
+    if(logged == "Yes"){
+
+      df <- filter(df, tx == "Active") %>%
+        select(subj_id, tx, ep, bl) %>%
+        mutate(ep = log(ep), bl = log(bl))
+
+      df <- full_join(
+        select(df, subj_id, bl) %>% filter(!is.na(bl)), 
+        select(df, subj_id, ep) %>% filter(!is.na(ep)), 
+        by = "subj_id"
+      ) %>%
+        filter(!is.na(bl) & !is.na(ep))
+    }
+
+    if(logged == "No"){
+
+       df <- filter(df, tx == "Active") %>%
+        select(subj_id, tx, ep, bl)
+
+      df <- full_join(
+        select(df, subj_id, bl) %>% filter(!is.na(bl)), 
+        select(df, subj_id, ep) %>% filter(!is.na(ep)), 
+        by = "subj_id"
+      ) %>%
+        filter(!is.na(bl) & !is.na(ep))
+
+    }
+
+    sdx <- sd(df$ep, na.rm = TRUE) 
+    sdy <- sd(df$bl, na.rm = TRUE) 
+    n   <- nrow(df)
+    rho <- cor(df$ep, df$bl, use = "complete")
+
+    Qx <- sdx^2*(n-1)            
+    Qy <- sdy^2*(n-1)
+    Qxy <- rho*sdx*sdy*(n-1)
+  # This is from Sachs...same result. 
+  # Qxy2 <- sum(df$ep * df$bl, na.rm = TRUE) - ((sum(df$ep) * sum(df$bl))/n) 
+    num <- (Qx-Qy)*sqrt(n-2)          # Statistic numerator
+    den <- 2*sqrt(Qx*Qy-Qxy^2)        # Statistic denominator
+    Qest <- num/den # T
+
+    # LL2 <- qt(0.025, n-2)
+    # UL2 <- qt(0.975, n-2)
+    # greater.var.outQ <- sum(Qest < LL2) 
+    # lower.var.outQ <- sum(Qest > UL2)
+
+    if(Qest < 0){p <- pt(Qest, n-2) * 2}
+    if(Qest > 0){p <- pt(Qest, n-2, lower.tail = FALSE) * 2}
+
+    df <- data_frame(
+      var = var_lab, 
+      vr = signif(sdx^2/sdy^2, 2), 
+      p = round(p, 3)
+      )
+
+    return(df)
+
+    }
+
+# var_ratio(sbp, "SBP")
+
+  data_list <- list(sbp, dbp, c_sbp, c_dbp, art_stif, glu, hdl, ldl, oxldl,
+                    pwa_augment, tag, tchol)
+  varnames <- c("SBP", "DBP", "Central SBP", "Central SBP", 
+                "Arterial Stiffness", "Glucose", "HDL", "LDL", "OxLDL", 
+                "PWA Augment", "TAG", "Total Cholesterol")
+
+  df <- data.frame(
+    df = I(list(sbp, dbp, c_sbp, c_dbp, art_stif, glu, hdl, ldl, oxldl,
+                pwa_augment, tag, tchol)),
+    var_lab = c("SBP", "DBP", "Central SBP", "Central DBP", 
+                "Arterial Stiffness", "Glucose", "log(HDL)", "LDL", "log(OxLDL)", 
+                "PWA Augment", "log(TAG)", "log(Total Cholesterol)"), 
+    logged = c(rep("No", 6), "Yes", "No", "Yes", "No", "Yes", "Yes"),
+    stringsAsFactors = FALSE
+    )
+
+```
+
+```{r table3_vr_html, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
+
+  do.call(bind_rows, pmap(df, var_ratio)) %>%
+    flextable()
+
+```
+
+```{r table3_vr_word, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}
+
+  do.call(bind_rows, pmap(df, var_ratio)) %>%
+    knitr::kable()
+
+```
+
+```{r, vr_pm_test, eval = FALSE}
+
+# Same thing, but using the Pitman Morgan test. Exactly the same.
+
+  df <- filter(dbp, tx == "Active") %>%
+    select(subj_id, tx, ep, bl)
+
+  df <- full_join(
+    select(df, subj_id, bl) %>% filter(!is.na(bl)), 
+    select(df, subj_id, ep) %>% filter(!is.na(ep)), 
+    by = "subj_id"
+    )
+
+  PairedData::Var.test(df$ep, df$bl, paired = TRUE)
+
+```
+
+```{r withn_sd, eval = FALSE}
+
+  df <- filter(sbp, tx == "Control") 
+  df <- full_join(
+     select(df, subj_id, bl) %>% filter(!is.na(bl)), 
+     select(df, subj_id, ep) %>% filter(!is.na(ep)), 
+     by = "subj_id"
+  ) %>%
+    mutate(diff = ep - bl)
+
+  sd(df$diff, na.rm = TRUE)
+
+```

### 2020-01-05 scripts/01_project.R

@@ -1,9 +1,13 @@
 
+# This runs all the scripts neccessary to create the data and models that are
+# then reported in the paper_stats.rmd file.
+
+
   source("scripts/02_functions.R")
 
   source("scripts/03_data.R")
 
-  source("scripts/04_primary_outcome.R")
+  source("scripts/04_primary_outcomes.R")
 
   source("scripts/05_secondary_outcomes.R")
 

### 2020-01-05 scripts/02_functions.R

@@ -1,5 +1,9 @@
 
-
+# These scripts includes a number of functions used in the analysis. Namely,
+# there are functions to quickly reshape the main data set for each of the
+# study outcomes as needed; and to plot said data in a manner that makes sense
+# for a cross over trial. There are also functions for creating the main
+# table 1 for the paper.
 
 # Outcome data prep ------------------------------------------------------------
 
@@ -52,7 +56,7 @@
     return(df)
   }
 
-# Outcome cross-over plot ####
+# Outcome cross-over plot ------------------------------------------------------
 
   cross_plot <- function(df, ylabel,logged = c("yes", "no"), ...){
 
@@ -106,7 +110,7 @@
   }
 
 
-# OUtcome distribution plot ####
+# Outcome distribution plot ----------------------------------------------------
 
   dist <- function(data, ylabel, logged = c("yes", "no"), ...){
 
@@ -137,7 +141,7 @@
     }
   }
 
-# Others ####
+# Others -----------------------------------------------------------------------
 
   is_labelled <- function(x) {
     if (length(class(x)) > 1) return(any(class(x) == "labelled"))
@@ -157,212 +161,11 @@
     return(x)
   }
 
-# User defined functions ####
 
-  num <- function(x){
-    x <- as.numeric(gsub("[:alpha:]", "", x))
-    return(x)
-  }
-
-# Extract labels from class = labelled data
-
-  extract.labels <- function(x){attributes(attributes(x)$labels)$names}
-
-# Explore data one variable at a time
-
-  class.slow <- function(data, ...) {
-
-    for (i in seq_along(1:length(data))) {
-
-      readline(prompt = "Press [enter] to continue")
-
-      require(dplyr)
-
-      print(i)
-      names(data[i])   %>% print()
-      class(data[[i]]) %>% print()
-      length(levels(factor(data[[i]]))) %>% print()
-
-      readline(prompt = "Press [enter] to continue")
-
-      if(length(levels(factor(data[[i]]))) < 20){ table(data[i]) %>% print()}
-
-      tryCatch({
-
-        summarise_(data[i],
-                   obs  = ~n(),
-                   mean = ~mean(data[[i]], na.rm = TRUE),
-                   min  = ~min(data[[i]], na.rm = TRUE),
-                   max  = ~max(data[[i]], na.rm = TRUE)) %>%
-          print()
-
[…]

### 2020-01-05 scripts/03_data.R

@@ -1,4 +1,8 @@
 
+# This script fixes up the data sent by the investigator (see project /data
+# folder)
+
+
   library(tidyverse)
 
 # Data -------------------------------------------------------------------------
@@ -56,10 +60,20 @@
     gsub("p_2", "p2", .) %>%
     gsub("_bl_", "_b_", .)
 
+# Add factor levels
+
+# table(data$educationcategory)
+  labs <- c("Primary school", "Secondary school", "University degree",
+            "Other professional qualification")
+  data <- mutate(data, educationcategory = factor(educationcategory, labels = labs))
+
+# table(data$occupation)
+  labs <- c("Professional/managerial/technical",
+            "Non-manual skilled",
+            "Manual skilled",
+            "Semi skilled/unskilled (including students)",
+            "Not disclosed")
+
+  data <- mutate(data, occupation = factor(occupation, labels = labs))
+
 # save(data, file = gsub(" ", "_", paste0("data_", date(), ".RData")))
-
-
-
-
-
-

### 2020-01-05 scripts/04_primary_outcomes.R

@@ -1,4 +1,8 @@
 
+# This script runs the key multilevel models for each of the nominated primary
+# outcomes. It also has code for producing plots as needed.
+# 05_secondary_outcomes.R does the same for the other outcomes.
+
   library(tidyverse)
   library(lme4)
   library(sjPlot)
@@ -40,6 +44,13 @@
 #        scale = 0.6, dpi = 600)
 
 # Models ####
+
+# Because we want to option for period specific baseline adjustment for the
+# given outcome, we first bl and ep specific values and delete the missings then
+# rejoin them; then mean center the bl value. Using the resulting dataframe, we
+# estimate 4 models: sex adjusted; +period effect; + tx by period interaction;
+# + and then a "final" model with sex, period, and baseline (no interactions).
+# A table for these models can be nicely done with sjPlot::tab_models as needed.
 
   me_sbp_df <- full_join(
     select(sbp, subj_id, sex, period, bl, tx) %>% filter(!is.na(bl)),

### 2020-01-24 paper_stats.Rmd
update after dropping exclusions

@@
 output: 
-  word_document:
-    reference_docx: style.1.docx
   html_document:
@@
 
-To evalaute the possilbity of heterogeneity of treatment effects, we followed the advice of Cortes et al.
-(REF) and calulated the various outcome variances for the baseline and end-of-period values under the active treatment condtion, and tested wheher the resulting outcome-specific variance ratios were equal to 1 using a two-sided Pitman Morgan test for paired observations (REF).
+To evaluate the possibility of heterogeneity of treatment effects, we followed the advice of Cortes et al.
+(REF) and calculated the various outcome variances for the baseline and end-of-period values under the active treatment condition, and tested whether the resulting outcome-specific variance ratios were equal to 1 using a two-sided Pitman Morgan test for paired observations (REF).
 We reported exact p-values from this test.
@@
 
-Heterogenity
+Heterogeneity
 

### 2020-01-24 scripts/02_functions.R

@@ -53,6 +53,20 @@
     df$time2 <- factor(df$time, labels = c("p1_b", "p1_ep",
                                            "p2_b", "p2_ep"))
 
+    df <- full_join(
+      filter(df, timing == "Baseline" & tx == "Active" & !is.na(bl)) %>%
+        select(subj_id, bl_act = bl),
+      filter(df, timing == "Baseline" & tx == "Control" & !is.na(bl)) %>%
+        select(subj_id, bl_con = bl),
+      by = "subj_id"
+    ) %>% full_join(
+      filter(df, timing == "EoP" & tx == "Control" & !is.na(ep)) %>%
+        select(subj_id, ep_con = ep),
+      by = "subj_id"
+    ) %>% mutate(regular = rowMeans(.[c("bl_act", "bl_con", "ep_con")])) %>%
+      select(subj_id, regular) %>%
+      full_join(df)
+
     return(df)
   }
 
@@ -61,8 +75,14 @@
   cross_plot <- function(df, ylabel,logged = c("yes", "no"), ...){
 
     if(logged == "no"){
+      plt <- ggplot(df, aes(x = time2, y = value, group = subj_id))
+    }
 
-    return(ggplot(df, aes(x = time2, y = value, group = subj_id)) +
+    if(logged == "yes"){
+      plt <- ggplot(df, aes(x = time2, y = log(value), group = subj_id))
+    }
+
+    plt <- plt +
       geom_line(data = filter(df, as.numeric(time) < 3), alpha = 0.2,
                 aes(color = treatment_p1)) +
       geom_smooth(data = filter(df, as.numeric(time) < 3), method = "lm",
@@ -80,33 +100,10 @@
       theme(panel.grid.major = element_blank()) +
       scale_x_discrete(labels = c("Start P1", "End P1", "Start P2", "End P2")) +
       xlab("") +
-      ylab(ylabel))
+      theme_minimal() +
+      ylab(ylabel)
 
-    }
-
-    if(logged == "yes"){
-
-      return(ggplot(df, aes(x = time2, y = log(value), group = subj_id)) +
-        geom_line(data = filter(df, as.numeric(time) < 3), alpha = 0.2,
-                  aes(color = treatment_p1)) +
-        geom_smooth(data = filter(df, as.numeric(time) < 3), method = "lm",
-                    aes(color = treatment_p1, linetype = treatment_p1,
-                        group = treatment_p1),
-                    se = FALSE, size = 2) +
[…]

### 2020-01-24 scripts/03_data.R

@@ -35,6 +35,7 @@
 
   data <- unlabel(data)
 
+
 # Remove NaNs
 
   data[sapply(data, is.numeric)] <- apply(data[sapply(data, is.numeric)], 2,
@@ -76,4 +77,10 @@
 
   data <- mutate(data, occupation = factor(occupation, labels = labs))
 
-# save(data, file = gsub(" ", "_", paste0("data_", date(), ".RData")))
+# Remove poor comlpliance and observation with cholesterol meds
+
+  data <- filter(data, subj_id != "R031") # Complicance View(filter(data, pc_compliance_p1 < 80))
+  data <- filter(data, as.numeric(dropout) == 0) # Dropout
+  data <- filter(data, statin_use_study == 0) # Statin use
+
+  # save(data, file = gsub(" ", "_", paste0("data_", date(), ".RData")))
